Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-09-21 parts-models-ph-php.tex
typo

In \pref{def:fop}, we define the the operator $\Fopsymbol$ which characterises the playability of an action
given the semantics of AAN$k$s (see \pref{def:playp}).
This operator simply states that the hitters of an action have to be active,
and every other action of higher priority must not be playable.

>>>>

In \pref{def:fop}, we define the operator $\Fopsymbol$ which characterises the playability of an action
given the semantics of AAN$k$s (see \pref{def:playp}).
This operator simply states that the hitters of an action have to be active,
and every other action of higher priority must not be playable.
